Disparity peaks

### 2018-02-06 analyses/07-figure-peaks.Rmd
Correct output name for figure 3

pdf("../manuscript/figures/fig-peaks-epoch-revision.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))

>>>>

pdf("../manuscript/figures/Figure3-fig-peaks-epoch-revision.pdf")  
  multiplot(beck_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            brusatte_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_peaks + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            wright_peaks + theme(plot.margin=unit(c(5.5, 5.5, 20, 25),"points")),
            cols = 1,
            labs = list("Time bins or time slice method",
                        "Time at disparity peak (MYA)"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))
